---
title: "inmetr"
author: "Jonatan Tatsch"
date: "July 8, 2016"
output: 
  html_document: 
    keep_md: yes
---

```{r0 setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
```

`inmetr` provide access to the "Banco de Dados Meteorológicos para Ensino e Pesquisa" ([BDMEP](http://www.inmet.gov.br/projetos/rede/pesquisa/)) do Instituto Nacional de Meteorologia ([INMET](http://www.inmet.gov.br)).



# Instalation

Installation of inmetr from GitHub is easy using the devtools package.

```{r, comment="", eval = TRUE, message=FALSE, error=FALSE}
library(devtools)
install_github('jdtatsch/inmetr')
```

```{r, comment="", message=FALSE}
library(inmetr)
library(dplyr)
```

## Station metadata

To search for meteorological station from INMET the user can use the `bdmep_info()` function.

```{r, comment=""}
info <- bdmep_info()
head(info)
str(info)
```

This function will return all site names, state and OMM code. The OMM code is necessary to download data from a meteorological station.

Here we want to know the OMM code for the meterological station at Santa Maria in Rio Grande do Sul state.

```{r, comment=""}
code <- info %>% 
   filter(nome == "SANTA MARIA") %>%
   select(codigo_omm) %>%
   t() %>% c()
code
```

## Import data

```{r, eval=FALSE}
sm <- import_bdmep(stn_id = code, 
                   e_mail = "seu-email",
                   passwd = "sua-senha",
                   save_file = FALSE, 
                   import = TRUE)
head(sm)
str(sm)
```


```{r, eval=TRUE, echo=FALSE}
sm <- import_bdmep(stn_id = code, 
                   e_mail = "jdtatsch@gmail.com",
                   passwd = "d17ulev5",
                   save_file = FALSE, 
                   import = TRUE)
head(sm)
str(sm)
```


