---
title: "Import data from BDMEP-INMET"
author: "Jônatan Tatsch"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Import data from BDMEP-INMET}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

`inmetr` provide acces to the Banco de Dados Meteorológicos para Ensino e Pesquisa ([BDMEP](http://www.inmet.gov.br/projetos/rede/pesquisa/)) do Instituto Nacional de Meteorologia ([INMET](http://www.inmet.gov.br)).

## Installation

Installation of inmetr from GitHub is easy using the devtools package.

```{r, comment="", include=FALSE}
library(devtools)
#install_github('jdtatsch/inmetr')
library(inmetr)
```


## Station metadata

To search for meteorological station from INMET the user can use the `bdmep_info()` function.

```{r, comment="", include=FALSE}
info <- bdmep_info()
info
```

This function will return all site names, state and OMM code. The OMM code is necessary to download data from one meteorological station.

Here we want to know the OMM code for the meterological station at Santa Maria in Rio Grande do Sul state.

```{r, comment="", include=FALSE}
code <- info %>% 
  filter(nome == "SANTA MARIA") %>%
  select(codigo_omm) %>%
  t() %>% c()
code
```

## Import data

```{r, include=FALSE}
sm <- import_bdmep(stn_id = code, 
                   e_mail = "seu-email",
                   passwd = "sua-senha",
                   save_file = FALSE, 
                   import = TRUE)
sm
summary(sm)
```

